### 2024-08-27 paper/main.tex
fixed typo

There have only been a handful of papers to examine indecisions, which involve either high \autocite{lokeshHumansUtilizeSensory2022} or low time pressure \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016,philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}. We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokeshHumansUtilizeSensory2022}. In this competitive scenario, the ‘predator’ attempted to end up in the same target as the ‘prey’ by a time constraint, while the prey attempted to end up in the opposite target as the predator. This task had a high time pressure, such that participants were award ed no points if they were indecisive by failing to enter either target within the time constraint. The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision. Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions. Similar to others \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016, philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions. Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline. Yet the mechanisms that give rise to indecisive behaviour, which is particularly relevant under common high time pressure scenarios, remains unclear.

>>>>

There have only been a handful of papers to examine indecisions, which involve either high \autocite{lokeshHumansUtilizeSensory2022} or low time pressure \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016,philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}. We recently found a high proportion of indecisions during a competitive decision-making task between two humans that observed each other’s movements when selecting a target \autocite{lokeshHumansUtilizeSensory2022}. In this competitive scenario, the ‘predator’ attempted to end up in the same target as the ‘prey’ by a time constraint, while the prey attempted to end up in the opposite target as the predator. This task had a high time pressure, such that participants were awarded no points if they were indecisive by failing to enter either target within the time constraint. The task poses a conundrum: it may be advantageous to wait for future sensory information and react to an opponent, but it could also be better to switch from reacting to guessing before the time constraint to avoid an indecision. Surprisingly, participants displayed a median indecision rate of approximately 25\% with an upper range close to 40\% indecisions. Similar to others \autocite{karsilarSpeedAccuracyTradeoff2014, wuCapacityCognitiveControl2016, philiastidesCausalRoleDorsolateral2011, dambacherTimePressureAffects2015,forstmannStriatumPreSMAFacilitate2008}, Karsilar and colleagues (2014) used a low time pressure task and found only 1.7\% of trials were indecisions. Tasks with low time pressure are characterized by providing relatively strong sensory information well in advance of the time constraint deadline. Yet the mechanisms that give rise to indecisive behaviour, which is particularly relevant under common high time pressure scenarios, remains unclear.
